\documentclass{article}
\usepackage[accepted]{icml2018}

\icmltitlerunning{Report Title}

\begin{document}

\twocolumn[
\icmltitle{E0:270 - Machine Learning - Report Title}

\icmlsetsymbol{equal}{*}

\begin{icmlauthorlist}
\icmlauthor{List}{dep1}
\icmlauthor{Names}{dep2}
\icmlauthor{Alphabetically}{dep1}
\end{icmlauthorlist}

\icmlaffiliation{dep1}{Department of Computer Science and Automation, Indian Insitute of Science, Bangalore}
\icmlaffiliation{dep2}{Mathematics Department, Indian Insitute of Science, Bangalore}

\icmlcorrespondingauthor{List}{your@email.address}
\icmlcorrespondingauthor{Names}{your@email.address}
\icmlcorrespondingauthor{Alphabetically}{your@email.address}

\icmlkeywords{keywords, related, to, your, project, like, pruning, gaussian process, etc.}

\vskip 0.3in
]

\printAffiliationsAndNotice{}

\begin{abstract}
The abstract should be ideally less than 10 short sentences. Among other things, provide information about what is your objective and how much progress has been made. 
\end{abstract}

\section{Introduction}
\label{introduction}
The PDF report should contain at most two pages excluding references and appendix and at most four pages including everything. Write about a subset of the following things that applies to your project:

\begin{enumerate}
	\item Problem Statement
	\item Motivation
	\item Literature Review
	\item Model description
	\item Dataset description
	\item Preliminary Results
	\item Future Work
\end{enumerate}

You can additionally provide anything else that is relevant to your project but is not present in the list given above. 

You can create various sections/subsections etc. to organise your report as per the need. Use \texttt{biblio.bib} file to provide references. The references should be provided by using cite keyword \cite{langley00}.

You can contact your project mentor if you have any confusion.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage

\bibliography{biblio}
\bibliographystyle{icml2018}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Remove this part if you are not using an Appendix. Appendix is ungraded. The
% reader may wish to ignore the appendix altogether. Write everything that you
% think is important in the main report text only.

\appendix
\section{Optional Appendix (Ungraded)}
Remove this part if you are not using an Appendix. Appendix is ungraded. The
reader may wish to ignore the appendix altogether. Write everything that you
think is important in the main report text only.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}